---
title: "Phytophthora and Hosts in the UK and Globally"
author: ""
date: "" 
output: html_document 
#runtime: shiny

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = getwd())
library(DT)
library(raster)
library(knitr)
library(stringr)
library(dplyr)
library(kableExtra)
```


## Phytophthora~Host interactions in the UK for key host species


Includes unspecified phyto, so that can see if there is any other county in which the key host has been recorded with a Phyto, but where the phyto is an unspecified species the UK, Eng, Wal and Scot columns will read NA, given that we are unaware of which specific Phyto species is in question, and so cannot say whether it is the same unspecified species and host combination(s) that are in the UK.


<br>


```{r host_data, include=FALSE}


species <- read.csv("data/global_sp_key_host_phyto.csv", stringsAsFactors = FALSE)

genus <- read.csv("data/global_gen_key_host_phyto.csv", stringsAsFactors = FALSE)




```

  

```{r}
library(DT)

species_dt <- datatable(species,
                             rownames = FALSE,
                             filter = 'top')


genus_dt <- datatable(genus,
                             rownames = FALSE,
                             filter = 'top')

```

## {.tabset}

### Species{.tabset .col-leftmid}
```{r ,echo = FALSE}
species_dt   
```
##### {-}

### {-}

### Genus{.tabset .col-leftmid}
```{r ,echo = FALSE, warning = FALSE}
genus_dt   
```


##### {-}

### {-}

## {-}




<br>


