---
title: "Phytophthora and Hosts in the UK and Globally"
author: ""
date: "" 
output: html_document 
#runtime: shiny

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir = getwd())
library(DT)
library(raster)
library(knitr)
library(stringr)
library(dplyr)
library(kableExtra)
```


## Location of hosts of key phytophthora

 ***IT MAY TAKE A FEW SECONDS FOR THESE DATA TABLES TO LOAD***

Here we provide tables showing the locations of 

  # for this, must use the kew_species names rather than std_name_h, because
  # if we use std_name_h, we will not pick up all genus (as not all genus
  # are in std_name_h if they appear as a host in the database that is species
  # level only)
  # as we have primarily standardised names using kew, this should not be a particular
  # problem, but there may be some species/genus wihtin the database that are not allocated              # distribution information
  # if they were not standardised with the Kew data as the backbone


Where a host appears to have no record of a phyto in any of the locations for which it is shown, this will be
due to a record of a key phytophthora being on that host from a location that Kew has not 
listed has being a location in which that host is found. e.g., P. cinnamomi on Betula utilis in Australia



<br>


```{r host_data, include=FALSE}


species_l1 <- read.csv("data/host_loc_sp_level1.csv", stringsAsFactors = FALSE)

species_l2 <- read.csv("data/host_loc_sp_level2.csv", stringsAsFactors = FALSE)

species_l3 <- read.csv("data/host_loc_sp_level3.csv", stringsAsFactors = FALSE)

genus_l1 <- read.csv("data/host_loc_gen_level1.csv", stringsAsFactors = FALSE)

genus_l2 <- read.csv("data/host_loc_gen_level2.csv", stringsAsFactors = FALSE)

genus_l3 <- read.csv("data/host_loc_gen_level3.csv", stringsAsFactors = FALSE)


```

  

```{r}
library(DT)

species_l1_dt <- datatable(species_l1,
                             rownames = FALSE,
                             filter = 'top')

species_l2_dt <- datatable(species_l2,
                             rownames = FALSE,
                             filter = 'top')

species_l3_dt <- datatable(species_l3,
                             rownames = FALSE,
                             filter = 'top')

genus_l1_dt <- datatable(genus_l1,
                             rownames = FALSE,
                             filter = 'top')


genus_l2_dt <- datatable(genus_l2,
                             rownames = FALSE,
                             filter = 'top')

genus_l3_dt <- datatable(genus_l3,
                             rownames = FALSE,
                             filter = 'top') 
```

## {.tabset}

### Species{.tabset .col-leftmid}
#### Level.3 
```{r ,echo = FALSE}
species_l3_dt   
```
#### Level.2
```{r ,echo = FALSE}
species_l2_dt
```
#### Level.1
```{r ,echo = FALSE}
species_l1_dt
```
##### {-}

### {-}

### Genus{.tabset .col-leftmid}
#### Level.3 
```{r ,echo = FALSE, warning = FALSE}
genus_l3_dt   
```
#### Level.2
```{r ,echo = FALSE}
genus_l2_dt
```
#### Level.1
```{r ,echo = FALSE}
genus_l1_dt
```

##### {-}

### {-}

## {-}




<br>


