---
title: Phytophthora and Hosts in the UK and Globally
author: "Key Host Species"
date: ""
output: html_document
# css: styles.css
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(kableExtra)
library(purrr)
library(sf)
library(ggplot2)
library(leaflet)
library(stringr)
library(htmltools)
```



# global locations are based on data within the database as have not got a distribution dataset for phyto


## {.tabset}

### All Key Species{.tabset .col-leftmid}

#### WGSRPD Level 4
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/All_key_species_Level.4.html", width = "100%", style="height: 70vh;")
```
#### WGSRPD Level 3
```{r, echo = FALSE}
     htmltools::tags$iframe(src = "maps/All_key_species_Level.3.html", width = "100%", style="height: 75vh;")
```
#### WGSRPD Level 2
```{r, echo = FALSE}
     htmltools::tags$iframe(src = "maps/All_key_species_Level.2.html", width = "100%", style="height: 80vh;")
```
#### WGSRPD Level 1
```{r, echo = FALSE}
  htmltools::tags$iframe(src = "maps/All_key_species_Level.2.html", width = "100%", style="height: 85vh;")
```

### Alnus glutinosa{.tabset .col-leftmid}

#### WGSRPD Level 4
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_glutinosa_Level.4.html", width = "100%", style="height: 90vh;")
```
#### WGSRPD Level 3
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_glutinosa_Level.3.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 2
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_glutinosa_Level.2.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 1
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_glutinosa_Level.1.html", width = "100%", style="height: 100vh;")
```

### Alnus incana{.tabset .col-leftmid}

#### WGSRPD Level 4
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_incana_Level.4.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 3
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_incana_Level.3.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 2
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_incana_Level.2.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 1
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_incana_Level.1.html", width = "100%", style="height: 100vh;")
```

### Alnus rubra{.tabset .col-leftmid}

#### WGSRPD Level 4
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_rubra_Level.4.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 3
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_rubra_Level.3.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 2
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_rubra_Level.2.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 1
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Alnus_rubra_Level.1.html", width = "100%", style="height: 100vh;")
```

### Juniperus communis{.tabset .col-leftmid}

#### WGSRPD Level 4
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Juniperus_communis_Level.4.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 3
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Juniperus_communis_Level.3.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 2
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Juniperus_communis_Level.2.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 1
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Juniperus_communis_Level.1.html", width = "100%", style="height: 100vh;")
```

### Larix decidua{.tabset .col-leftmid}

#### WGSRPD Level 4
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Larix_decidua_Level.4.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 3
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Larix_decidua_Level.3.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 2
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Larix_decidua_Level.2.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 1
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Larix_decidua_Level.1.html", width = "100%", style="height: 100vh;")
```

### Larix x eurolepis{.tabset .col-leftmid}

#### WGSRPD Level 4
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Larix_x_eurolepis_Level.4.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 3
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Larix_x_eurolepis_Level.3.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 2
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Larix_x_eurolepis_Level.2.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 1
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Larix_x_eurolepis_Level.1.html", width = "100%", style="height: 100vh;")
```

### Pinus sylvestris{.tabset .col-leftmid}

#### WGSRPD Level 4
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Pinus_sylvestris_Level.4.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 3
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Pinus_sylvestris_Level.3.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 2
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Pinus_sylvestris_Level.2.html", width = "100%", style="height: 100vh;")
```
#### WGSRPD Level 1
```{r, echo = FALSE}
    htmltools::tags$iframe(src = "maps/Pinus_sylvestris_Level.1.html", width = "100%", style="height: 100vh;")
```



